### 2017-12-30 article.tex
appendix

Under JD’s current memorandum and articles of association, our board of directors will not be able to form a quorum without Mr. Richard Qiangdong Liu for so long as Mr. Liu remains a director.(Page118)

@@

Gross profit decreased 0.768 in fiscal year 2016. It suggests weaker sales and therefore excess inventory. The Group sold inventories rather slower compared to the fiscal year 2015.

@@

Net cash provided by operating activities increased by \textyen7,070,695,000, a 417\% increase.  
The net cash used in investing activities increases by \textyen42,478,052,000 from FY 2015 to FY 2016. Therefore, the net cash used in investing activities increases by nearly 734\% from FY 2006 to FY 2007
The net cash provided in financing activities increased by \textyen35,999,198,000 from FY 2015 to FY 2016. Thus, this shows a 766\% increase in net cash used in financing activities.
These changes are dramatic. From Consolidated Statements of Cash Flows, we can find the main reasons for each change:
The increase of net cash provided by operating activities is mainly due to the decrease of net loss. It indicates better performance of JD in operating activities.
The increase of the net cash used in investing activities is mainly caused by purchasing of other investments and paying for loan originations. It indicates that JD is increasing investment. And it also indicates the effect of JD Finance has changed from supporting the overall JD platform to an independently operated and self-funded business.
The increase of net cash provided by financing activities is mainly because of Proceeds from sales of financial products and Capital injection from non-controlling interest shareholders compared with the previous year. It also indicates part of the effect of JD Finance has changed from supporting the overall JD platform to an independently operated and self-funded business.

>>>>

Under JD’s current memorandum and articles of association, our board of directors will not be able to form a quorum without Mr. Richard Qiangdong Liu for so long as Mr. Liu remains a director\footnote{See JD.com, Inc. annual report 2016, Page 118}.

@@

Inventory turnover decreased 0.768 in fiscal year 2016. It suggests weaker sales and therefore excess inventory. The Group sold inventories rather slower compared to the fiscal year 2015.

@@

Net cash provided by operating activities increased by \textyen7,070,695,000, a 417\% increase.

The net cash used in investing activities increases by \textyen42,478,052,000 from FY 2015 to FY 2016. Therefore, the net cash used in investing activities increases by nearly 734\% from FY 2006 to FY 2007
The net cash provided in financing activities increased by \textyen35,999,198,000 from FY 2015 to FY 2016. Thus, this shows a 766\% increase in net cash used in financing activities.

These changes are dramatic. From Consolidated Statements of Cash Flows, we can find the main reasons for each change:
\begin{itemize}
\item The increase of net cash provided by operating activities is mainly due to the decrease of net loss. It indicates better performance of JD in operating activities.

\item The increase of the net cash used in investing activities is mainly caused by purchasing of other investments and paying for loan originations. It indicates that JD is increasing investment. And it also indicates the effect of JD Finance has changed from supporting the overall JD platform to an independently operated and self-funded business.

\item The increase of net cash provided by financing activities is mainly because of Proceeds from sales of financial products and Capital injection from non-controlling interest shareholders compared with the previous year. It also indicates part of the effect of JD Finance has changed from supporting the overall JD platform to an independently operated and self-funded business.

\end{itemize}
